(\cite{Hartley.2011})
\begin{itemize}
\item use Markus Mann - StereoCameraCalibration.pdf !!!!
\item and Camera Calibration for Stereo Vision.pdf
\item Disparity
\item Rectification
\item Triangulation?
\item Levenberg-Marquardt algorithm? \url{http://www.cs.ubc.ca/~lowe/papers/danm96.pdf}
\item RANSAC?
\end{itemize}

%------------------------------
\section{Projective Geometry}
%------------------------------
\subsection{Coordinate Systems}

\subsection{Camera Models}
\subsubsection{Extrinsic parameters}
\subsubsection{Intrinsic paramters}

%------------------------------
\section{Epipolar Geometry}
%------------------------------
\subsection{Aufbau}
\subsection{Essential matrix}
\index{Essential matrix}
\subsection{Fundamental matrix}
\index{Fundamental matrix}
\enquote{In der Theorie benötigt der 8-Punkt-Algorithmus mindestens acht korrespondierende Punkte für die Berechnung der Fundamental-Matrix. Allerdings wird dabei eine hohe Genauigkeit der Werte vorausgesetzt. Bei einer manuellen Bestimmung der Punkte, hat es sich als sinnvoll herausgestellt, mehr als acht Korrespondezen zu wählen.}


%------------------------------
\section{3-D reconstruction}
%------------------------------

\subsection{Structure from motion}\label{ssec:SfM}
\subsection{Stereo matching}\label{ssec:stereoMatch}






 
\section{Disparity}

\begin{itemize}
\item Disparity Map
\end{itemize}

"Disparity refers to the distance between two corresponding points in the left and right image of a stereo pair. Obviously this process involves choosing a point in the left hand frame and then finding its match (often called the corresponding point) in the right hand image; often this is a particularly difficult task to do without making a lot of mistakes. A useful topic to read about when performing stereo matching is rectification. This will make the process of matching pixels in the left and right image considerably faster as the search will be horizontal."
(http://stackoverflow.com/questions/17607312/difference-between-disparity-map-and-disparity-image-in-stereo-matching)

\section{Rectification}
